Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-09-19 paper/paper.tex
Move human judgments section to backmatter

\subsection{Reducing Expert judgments of technique peculiarities}

@@

%%%%%%%%%%%%%% CROWDSOURCED JUDGMENTS OF PAIRWISE SIMILARITY %%%%%%%%%%%%%%%%%%%%
\subsection{Crowdsourced judgments of pairwise similarity}

@@

\subsection{Analysis}\label{sec:analysis}

>>>>

\section*{Reducing Expert judgments of technique peculiarities}

\ja{This needs to be summarized (possible in the previous section).
I'm copying two sentences in here that I had in the Timbre similarity judgments section.}%
These IPTs were selected from a larger set of $235$ IPTs by two experts at the \emph{Conservatoire national sup\'erieur de musique et de danse de Paris} (CNSMDP).
The selection criteria were based on the likelihood of an IPT being similar to some other IPT, ensuring that IPTs that were too singular were excluded from the survey.

@@

%%%%%%%%%%%%%% CROWDSOURCED JUDGMENTS OF PAIRWISE SIMILARITY %%%%%%%%%%%%%%%%%%%%
\section*{Crowdsourced judgments of pairwise similarity}

\ja{A lot of this is covered in the main text.
Not sure what we need to add in the appendix.}

@@

\section*{Analysis}\label{sec:analysis}

\ja{I thought all of this stuff was going away and we were just replacing it with a brief analysis using the tag clouds (and so on).
At any rate, the relevant analysis results should be in the main text (under Timbre similarity judgments, after we describe the experiments).}%
